\documentclass{article}
\usepackage{aurical}
\usepackage[T1]{fontenc}
\usepackage{pifont}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdfpagemode=FullScreen,
    }

\renewcommand{\labelitemiii}{-}
\renewcommand{\labelitemi}{-}

\begin{document}
\title{\textbf{AML: Notes on final project}}

\maketitle
%\Fontauri\slshape
\large

\begin{itemize}
\item Notes on first paper (Zagoruyko):

\begin{itemize}
\item Many different architectures, maybe use one or two best results and try to reproduce.
\item Very focused on patch matching / segmentation, not sure, how much feature matching (or wide baseline stereo matching) was done in this paper
\item Use of 64x64 patches: Makes it difficult for us to reproduce, since we have full resolution images. We need to decide on a way to pre-process our dataset or implement layers in the architecture that allow us to give different sizes as inputs (SPP layer?).
\item Interesting take on CNNs \& NCCs, maybe we could give NCC nerworks a try, since it takes care of the normalization.
\item Could use the Stretcha et al paper/data set to verify our results (comparing Zagoruyko with our network).
\item Doesn't exactly correspond to our task, since output of networks are depth maps and not camera positions. We need some idea to translate depth information to positional info.
\item We don't have the same ground truth as the data sets used in the paper. Our ground truth consists of positional information, not depth $\rightarrow$ can only take inspiration from this, but doesn't solve our problem.
\end{itemize}

\item Notes on "Understanding the Limitations of CNN-based Absolute Camera Pose Regression"
\begin{itemize}
\item main focus und single image based absolute 3D
\item "Image Retrieval" is closest to kaggle winners, since it basically uses the CNN for matching the test image with the most similar training image and using feature matching to estimate the relative position of the 2 images. RPR is basically kaggle challenge
\end{itemize}



\item Some more interesting links:
\begin{itemize}
\item Blogpost with basic info about Task+many useful resources \url{https://ducha-aiki.github.io/wide-baseline-stereo-blog/2020/03/27/intro.html}
\item Stretcha, Hansen: 3D reconstruction \url{https://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=4587706}
\item kaggle challenge winners \url{https://ducha-aiki.github.io/wide-baseline-stereo-blog/2022/07/05/IMC2022-Recap.html}
\item Sattler, Zhou: Understanding the Limits of CNN...\url{https://arxiv.org/abs/1903.07504}
\item Balntas, Li: RelocNet: \url{https://openaccess.thecvf.com/content_ECCV_2018/papers/Vassileios_Balntas_RelocNet_Continous_Metric_ECCV_2018_paper.pdf}
\item Laskar, Melekhov: Pairwise Relative Poses with CNN: \url{https://arxiv.org/pdf/1707.09733.pdf}´
\end{itemize}

\end{itemize}


\end{document}